---
title: "Pa4"
subtitle: "⚔<br/>with xaringan"
author: "Esther Hur"
date: "2018/3/2"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```
---
#### Load the dataset from your index.Rmd file.
```{r}
library(tidyverse)

my_fricatives <- read_csv("../data_raw/fricatives/fricatives.csv")
str(my_fricatives)
head(my_fricatives)
```
---
####Tidy the data
```{r}
data1 <- my_fricatives %>%
gather(., key = "category", value = "values",-obs, na.rm = TRUE,
       convert = FALSE, factor_key = FALSE) %>%
       separate(., col = category , into = c('phon', 'variable'), sep = "_") %>%
  spread(., key =variable, value =values)
```
---
####Provide a table of descriptive statistics

S  | Mean | Standard deviation |  Median
------------- | ------------- | ------------- | -------------
COG  | `r mean(my_fricatives$s_cog)`  | `r sd(my_fricatives$s_cog)` | `r median(my_fricatives$s_cog)`
Skewness  | `r mean(my_fricatives$s_skewness)`  | `r sd(my_fricatives$s_skewness)` | `r median(my_fricatives$s_skewness)`

SH  | Mean | Standard deviation |  Median
------------- | ------------- | ------------- | -------------
COG  | `r mean(my_fricatives$sh_cog)`  | `r sd(my_fricatives$sh_cog)` | `r median(my_fricatives$sh_cog)`
Skewness  | `r mean(my_fricatives$sh_skewness)`  | `r sd(my_fricatives$sh_skewness)` | `r median(my_fricatives$sh_skewness)`
---
##### Make a boxplot
```{r}
data1 %>%
  ggplot(., aes( x = phon, y = cog, fill = phon)) +
  geom_boxplot()
  labs( x= 'Phoneme', y = 'Center of Gravity')
```
---
```{r}  
ggplot(data = data1, aes(x = phon, y = skewness)) +
  stat_summary(fun.data = mean_cl_boot, geom = 'pointrange') 
```
---
#####Fit a model that examines center of gravity as a function of skewness for the [s] segments 
```{r}
data_1 <- data1 %>% 
  filter(., phon == 's') 
data_1 %>% 
  ggplot(., aes(x = cog, y =skewness, color = skewness )) +
  geom_point() +
  geom_smooth( method = lm)
```
---
##### Make a table of the model summary.
```{r}
model1 <-lm(data = data_1, cog ~ skewness) 
   summary(model1)
```
---
###Residuals:

Min   |    1Q  | Median  |     3Q   |   Max 
------------- | ------------- | ------------- | -------------  | -------------
-1060.74 |  -21.72  |  58.96 |  123.00  | 405.24 

###Coefficients:

---   | Estimate | Std. Error | t value | p-vale 
------------- | ------------- | ------------- | -------------  | -------------     
(Intercept)  | 8027.2    |  212.3 |  37.80  | < 2e-16 ***
skewness     | 3029.1    |  259.1 |  11.69 | 7.69e-10 ***


Residual standard error | Multiple R-squared | Adjusted R-squared | F-statistic | p-value
------------- | ------------- | ------------- | ------------- | -------------
320.1 on 18 degrees of freedom | 0.8836 |  0.8771 | 136.6 on 1 and 18 DF | 7.691e-10
---
#####Check model diagnostics. Make plots.
```{r}
mean(model1$residuals)
```
#####Correlation Test
```{r}
cor.test(data_1$cog, model1$residuals)
```
---
#####Global Validation of Linear Model Assumptions
```{r}
library(gvlma)
gvmodel <- gvlma(x = model1) 
plot(gvmodel)
```
---
#####Write up the results (as if it were for a journal article).

##### “A linear model was assessed between the center of gravity as a function of skewness for the [s] segments. There was a positive correlation between the two variables, B = 3029.1, S = 259.1, p = 0.005. A scatterplot summarizes the results. Overall, there was a strong, positive correlation between cog as a function of skewness. A Pearson product-moment correlation coefficient was computed. There was a positive correlation between the two variables, t = 1.5399, df = 18, p-value = 0.141. In addition, a gvlma was run using the global tes on 4 degrees of fredom with a level of signicance = 0.05"
---

 